Summer 2025 ToDo

### 2025-06-02 Relations/Paper/Summer_2025_TODO.tex
Minor code update to reflect changes to wf.

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
\end{todolist}
\end{document}

>>>>

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit. 
  \item find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. 
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability. 
  \item Working on CR $\to$ CP. Low priority.  
\end{todolist}
\end{document}
